Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-15 article.tex
Reference to better superior listings

Listing~\ref{lst:create_generative_experiment_explicit} shows how to
set up this experiment:

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, frame=single,
  label = {lst:create_generative_experiment_explicit},
  caption = {
    Create the experiments to answer research question 1, 
    using explicit arguments.
  }
]
experiment <- create_experiment(
  inference_conditions = create_inference_conditions(
    model_type = "generative", 
    run_if = "always"
  ), 
  inference_model = create_inference_model(
   site_model = create_jc69_site_model(), 
   clock_model = create_strict_clock_model(), 
   tree_prior = create_yule_tree_prior()
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, frame=single,
  label = {lst:create_generative_experiment},
  caption = {
    Create the experiments to answer research question 1.
  }
]
experiments <- list(experiment)
\end{lstlisting}

@@

We will create a list of experiments as in 
listing~\ref{lst:create_generative_experiment},
but with all defaults:

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, 
  frame=single,
  label = {lst:create_gen_experiment_defaults},
  caption = Create a list of one default generative experiment.
]
experiments <- list(create_gen_experiment())
\end{lstlisting}

@@

We choose again to use the default error measurement setup,
as shown in listing~\ref{lst:create_error_measure_params}.

>>>>

Listing~\ref{lst:create_gen_experiment_explicit} shows how to
set up this experiment:

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, frame=single,
  label = {lst:create_gen_experiment_explicit},
  caption = {
    Create the experiments to answer research question 1, 
    using explicit arguments.
  }
]
experiment <- create_experiment(
  inference_conditions = create_inference_conditions(
    model_type = "generative", 
    run_if = "always"
  ), 
  inference_model = create_inference_model(
   site_model = create_jc69_site_model(), 
   clock_model = create_strict_clock_model(), 
   tree_prior = create_yule_tree_prior()
  )
)
\end{lstlisting}

@@

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, frame=single,
  label = {lst:create_gen_experiment},
  caption = {
    Create the experiments to answer research question 1.
  }
]
experiments <- list(experiment)
\end{lstlisting}

@@

We will create an experiment as in 
listing~\ref{lst:create_gen_experiment},
but with all defaults:

\begin{lstlisting}[
  language=R, 
  floatplacement=ht, 
  frame=single,
  label = {lst:create_gen_experiment_defaults},
  caption = Create a list of one default generative experiment.
]
experiment <- create_gen_experiment()
\end{lstlisting}

Creating the complete set of experiments:

YYYYYYYYYYYYYYYYYYYYYYYYYYYYYYYY
experiments <- list(experiment)

@@

We choose again to use the default error measurement setup,
as shown in listing~\ref{lst:create_error_measure_params},
which is the default in \verb;create_pir_params;, so we'll
leave it out for now.
